showData 4

### 2016-11-08 CreateData/showData4.Rmd
cosmetics

They need to be of the right age (born on November 1, 1930 or earlier). We
get the birthdates from *inddata*.

@@

They need to be of the right age (born on November 1, 1935 or earlier). We
get the birthdates from *inddata*.

@@

@@

@@

This is no longer the last FoB we are using: The follow-up time this time
*is* ten years (as before), from November 1, 1990 to October 31, 2000, when
the *lisa* data has been filling in for a long time.

@@

>>>>

@@

@@

They need to be of the right age (born on November 1, 1955 or earlier). We
get the birthdates from *inddata*.

@@

They need to be of the right age (born on November 1, 1965 or earlier). We
get the birthdates from *inddata*.

@@

This is no longer the last FoB we are using: The follow-up time this time
*is* ten years (as before), from November 1, 1990 to December 31, 2001, when
the *lisa* data is filling in.

@@

They need to be of the right age (born on November 1, 1970 or earlier). We
get the birthdates from *inddata*.
